exp2_lik_by_trial

### 2021-06-04 Bayesian_models_exp1.Rmd
fixed Q learning bugs
added report in papaja and softmax to BCH models

---
title: "Bayesian_models_exp2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

dat <- subset(dat,human_id == "QSuzBXpbyRc370HsAACW")

@@

# if human generalizes over games, we can run update the prior generally
# if human does not generalize, we need to reset the prior at the start of each ?stage?
exp1_Bayes_model_LL <- function(par,data, generalize = c("game","no"), return_value = "-2loglik") {
   # return_value=c("-2loglik","likelihood_by_trial")
  # data is a subset for a single participant
  generalize <- match.arg(generalize)
  alpha <- par[1] # probability that ai opponent plays according to strategy
  if(length(par) > 1) {
    beta <- par[2] # probability that human plays according to best response 
  } else{
    beta <- 1 # probability that human plays according to best response 
  }

  prior <- c(1,1,1) # prior alpha for dirichlet on p(level)
  prior <- prior/sum(prior)

@@

  # now finally compute the likelihood of human actions 
  dat <- dat %>% 
    mutate(
      loglik = case_when(
        human_action_num == 1 ~ log(p_self_a1),
        human_action_num == 2 ~ log(p_self_a2),
        human_action_num == 3 ~ log(p_self_a3),
        human_action_num == 4 ~ log(p_self_a4),
        human_action_num == 5 ~ log(p_self_a5))
    )

@@

```{r}
exp1_Bayes_model_LL(0.4,data = dat, generalize = "no", "likelihood_by_trial")
```

@@

# # USing DEOptim 
for(id in levels(dat$human_id)) {
  tdat <- subset(dat,human_id == id)
  ctrl <- DEoptim.control(NP = 20, itermax=50,parallelType = 1, packages = c("dplyr"))
  exp1_Bayes_game_Tr[[id]] <- DEoptim(exp1_Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
                                  generalize = "game",control=ctrl)
  exp1_Bayes_no_Tr[[id]] <- DEoptim(exp1_Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
                                  generalize = "no",control=ctrl)
}

>>>>

---
title: "Bayesian_models_exp1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
```

@@

#dat <- subset(dat,human_id == "QSuzBXpbyRc370HsAACW")

@@

# if human generalizes over games, we can run update the prior generally
# if human does not generalize, we need to reset the prior at the start of each ?stage?
exp1_Bayes_model_LL <- function(par,data, generalize = c("game","no"), softmax= TRUE, return_value = "-2loglik") {

  # return_value=c("-2loglik","likelihood_by_trial")
  # input data for this function should be a subset for a single participant
  generalize <- match.arg(generalize)
  alpha <- par[1] # probability that ai opponent plays according to strategy

  if(softmax) {
    lambda <- par[2] # inverse temperature parameter in softmax function
  }

  beta <- 1 # probability that human plays according to best response 
  prior <- c(1,1,1) # prior alpha for dirichlet on p(level)
  prior <- prior/sum(prior)

@@

  #cat(as.character(c(round(dat$p_self_a1,2), "\n", "\n")))

  # now finally compute the likelihood of human actions 
  if (softmax) {

        dat <- dat %>% 
    mutate(sumexp = exp(lambda*p_self_a1) + exp(lambda*p_self_a2) + exp(lambda*p_self_a3) + exp(lambda*p_self_a4) + exp(lambda*p_self_a5)) %>%
             mutate(
               loglik = case_when(
                 human_action_num == 1 ~ log(exp(lambda*p_self_a1)/sumexp),
                 human_action_num == 2 ~ log(exp(lambda*p_self_a2)/sumexp),
                 human_action_num == 3 ~ log(exp(lambda*p_self_a3)/sumexp),
                 human_action_num == 4 ~ log(exp(lambda*p_self_a4)/sumexp),
                 human_action_num == 5 ~ log(exp(lambda*p_self_a5)/sumexp)
      )
    )
  } else {
    dat <- dat %>% 
    mutate(
      loglik = case_when(
        human_action_num == 1 ~ log(p_self_a1),
        human_action_num == 2 ~ log(p_self_a2),
        human_action_num == 3 ~ log(p_self_a3),
        human_action_num == 4 ~ log(p_self_a4),
        human_action_num == 5 ~ log(p_self_a5))
    )

@@

```{r}
# testing funcrion. Careful dat here can be all participants data, check how it is defined. 
exp1_Bayes_model_LL(c(0.4, 1) ,data = dat, generalize = "no", softmax = TRUE, "likelihood_by_trial")[51]
exp1_Bayes_model_LL(c(0.4) ,data = dat, generalize = "no", softmax = FALSE, "likelihood_by_trial")[51]
```
## Compare loglikelihood: probability matching vs softmax (with Between game transfer for now)

```{r echo=FALSE}
library(DEoptim)

prob_match_tr <- use_softmax_tr <- use_softmax_NT <- list()

# # Using DEOptim 
for(id in levels(dat$human_id)) {
  tdat <- subset(dat,human_id == id)
  ctrl <- DEoptim.control(NP = 20, itermax=50,parallelType = 1, packages = c("dplyr"))

  prob_match_tr[[id]] <- DEoptim(exp1_Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
                                  generalize = "game",FALSE, control=ctrl)

  use_softmax_tr[[id]] <- DEoptim(exp1_Bayes_model_LL, lower=c(0,0), upper = c(1,1000), data = tdat, generalize = "game",TRUE, control=ctrl)

  use_softmax_NT[[id]] <- DEoptim(exp1_Bayes_model_LL, lower=c(0,0), upper = c(1,1000), data = tdat, generalize = "no",TRUE, control=ctrl)

save(prob_match_tr,file="BCH_prob_match_tr.RData")
save(use_softmax_tr,file="BCH_use_softmax_tr.RData")
save(use_softmax_NT,file="BCH_use_softmax_NT.RData")
```

```{r}
compare_table <- data.frame()
for(id in levels(dat$human_id)) {
  compare_table <- rbind(compare_table,
                       data.frame(
                         "ID" = id,
                         "prob_match_tr_BIC" = prob_match_tr[[id]]$optim$bestval+ 1*log(150),
                         "softmax_tr_BIC" = use_softmax_tr[[id]]$optim$bestval+ 2*log(150)
                         ))
}

comp_models <- compare_table[c("ID","prob_match_tr_BIC","softmax_tr_BIC")]

BIC_weights_BCH <- comp_models["ID"]
BIC_weights_BCH[,2:ncol(comp_models)] <- t(apply(comp_models[,2:ncol(comp_models)], 1, function(i) exp(-0.5*(i-min(i)) )))
colnames(BIC_weights_BCH) <-colnames(comp_models)

BIC_weights_BCH[,2:ncol(BIC_weights_BCH)] <- t(apply(BIC_weights_BCH[,-1], 1, function(i) round(i/sum(i),2)))

colMeans(BIC_weights_BCH[,2:ncol(BIC_weights_BCH)])
```

@@

# # Using DEOptim 
for(id in levels(dat$human_id)) {
  tdat <- subset(dat,human_id == id)
  ctrl <- DEoptim.control(NP = 20, itermax=50,parallelType = 1, packages = c("dplyr"))
  exp1_Bayes_game_Tr[[id]] <- DEoptim(exp1_Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
                                  generalize = "game",control=ctrl)
  exp1_Bayes_no_Tr[[id]] <- DEoptim(exp1_Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
                                  generalize = "no",control=ctrl)
}

### 2021-06-04 Experiment_2/Bayesian_models_exp2.Rmd
added report in papaja and softmax to BCH models

# dat <- subset(dat,human_id == "bZg1T3MNoItL6b7qAAAj")
# dat <- subset(dat,human_id == "J3SqvTcFUwXtSC6wAAB0")
# dat <- subset(dat,human_id == "gRRZ0rUagyVejWTOAAFl")
dat <- subset(dat,human_id == "vGnDPRowetREQVmwAADL")
# dat <- subset(dat,human_id == "wi_zWhftr9MdqTmCAAHs")

@@

Bayes_model_LL <- function(par,data,distinct_opponent = TRUE, generalize = c("game","stage","no"), return = "-2loglik"){

  # data is a subset for a single participant
  generalize <- match.arg(generalize)
  alpha <- par[1] # probability that ai opponent plays according to strategy
  if(length(par) > 1) {
    beta <- par[2] # probability that human plays according to best response 
  } else{
    beta <- 1 # probability that human plays according to best response 
  }

@@

@@

```{r}
Bayes_model_LL(0.5,data = dat,distinct_opponent = TRUE, generalize = "game", return = "likelihood_by_trial")

@@

# USing DEOptim

for(id in levels(dat$human_id)) {
  tdat <- subset(dat,human_id == id)
  ctrl <- DEoptim.control(NP = 20, itermax=50)
  Bayes_same_game[[id]] <- DEoptim(Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
                                   distinct_opponent = FALSE, generalize = "game",control=ctrl)
  Bayes_same_stage[[id]] <- DEoptim(Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
                                   distinct_opponent = FALSE, generalize = "stage",control=ctrl)
  Bayes_same_no[[id]] <- DEoptim(Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
                                   distinct_opponent = FALSE, generalize = "no",control=ctrl)
  Bayes_distinct_game[[id]] <- DEoptim(Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
                                   distinct_opponent = TRUE, generalize = "game",control=ctrl)
  Bayes_distinct_stage[[id]] <- DEoptim(Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
                                        distinct_opponent = TRUE, generalize = "stage",control=ctrl)
  Bayes_distinct_no[[id]] <- DEoptim(Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
                                 distinct_opponent = TRUE, generalize = "no",control=ctrl)
}

# using optim

>>>>

# dat <- subset(dat,human_id == "bZg1T3MNoItL6b7qAAAj")
# dat <- subset(dat,human_id == "J3SqvTcFUwXtSC6wAAB0")
# dat <- subset(dat,human_id == "gRRZ0rUagyVejWTOAAFl")
#dat <- subset(dat,human_id == "vGnDPRowetREQVmwAADL")
# dat <- subset(dat,human_id == "wi_zWhftr9MdqTmCAAHs")

@@

Bayes_model_LL <- function(par,data,distinct_opponent = TRUE, softmax = TRUE, generalize = c("game","stage","no"), return = "-2loglik"){

  # data is a subset for a single participant

  generalize <- match.arg(generalize)
  alpha <- par[1] # probability that ai opponent plays according to strategy
  beta <- 1 # probability that human plays according to best response

  if(softmax) {
    lambda <- par[2] # inverse temperature parameter in softmax function
  }

@@

  # now finally compute the likelihood of human actions

    # now finally compute the likelihood of human actions 
  if (softmax) {

    dat <- dat %>% 
    mutate(sumexp = exp(lambda*p_self_a1) + exp(lambda*p_self_a2) + exp(lambda*p_self_a3)) %>%
             mutate(
               loglik = case_when(
                 human_action_num == 1 ~ log(exp(lambda*p_self_a1)/sumexp),
                 human_action_num == 2 ~ log(exp(lambda*p_self_a2)/sumexp),
                 human_action_num == 3 ~ log(exp(lambda*p_self_a3)/sumexp)
      )
    )

  } else {
    dat <- dat %>% 
    mutate(
      loglik = case_when(
        human_action_num == 1 ~ log(p_self_a1),
        human_action_num == 2 ~ log(p_self_a2),
        human_action_num == 3 ~ log(p_self_a3)
      )
    )

  }

@@

```{r}
Bayes_model_LL(c(0.5,1),data = dat,distinct_opponent = TRUE, generalize = "game", softmax = TRUE, return = "likelihood_by_trial")

@@

# Using DEOptim

for(id in levels(dat$human_id)) {
  tdat <- subset(dat,human_id == id)
  ctrl <- DEoptim.control(NP = 20, itermax=50,parallelType = 1, packages = c("dplyr"))

  # Here, optimisation implies softmax = TRUE as it was omitted as input and default is true 
  # Bayes_same_game[[id]] <- DEoptim(Bayes_model_LL, lower=c(0,0), upper = c(1,1000), data = tdat,
  #                                  distinct_opponent = FALSE, generalize = "game", control=ctrl)
  # 
  # Bayes_same_stage[[id]] <- DEoptim(Bayes_model_LL, lower=c(0,0), upper = c(1,1000), data = tdat,
  #                                  distinct_opponent = FALSE, generalize = "stage",control=ctrl)
  # 
  # Bayes_same_no[[id]] <- DEoptim(Bayes_model_LL, lower=c(0,0), upper = c(1,1000), data = tdat,
  #                                  distinct_opponent = FALSE, generalize = "no",control=ctrl)

  Bayes_distinct_game[[id]] <- DEoptim(Bayes_model_LL, lower=c(0,0), upper = c(1,1000), data = tdat,
                                   distinct_opponent = TRUE, generalize = "game",control=ctrl)

  Bayes_distinct_stage[[id]] <- DEoptim(Bayes_model_LL, lower=c(0,0), upper = c(1,1000), data = tdat,
                                        distinct_opponent = TRUE, generalize = "stage",control=ctrl)

  Bayes_distinct_no[[id]] <- DEoptim(Bayes_model_LL, lower=c(0,0), upper = c(1,1000), data = tdat,
                                 distinct_opponent = TRUE, generalize = "no",control=ctrl)
}

#save(prob_match_tr,file="BCH_prob_match_tr.RData")

# All these below use softmax for choice function rather than prob matching. For prob matching, choose softmax = FALSE above.
save(Bayes_distinct_game,file="Bayes_distinct_game.RData")
save(Bayes_distinct_stage,file="Bayes_distinct_stage.RData")
save(Bayes_distinct_no,file="Bayes_distinct_no.RData")

```{r}
# using optim

### 2021-06-04 Experiment_2/Experiment_2_modelling.Rmd
added report in papaja and softmax to BCH models

```
## Fitting ST_EWA_states WITHOUT transfer 
```{r, cache=TRUE}

@@

## Putting all results together 
```{r}
exp2_results <- data.frame()

@@

                         ########## MS results for Bayesian models
                          # Bayesian updating with between and within game transfer
                         "Distinct_game_BIC" = Bayes_distinct_game[[id]]$optim$bestval + 1*log(180),
                         "theta_transfer" = Bayes_distinct_game[[id]]$optim$bestmem[1],

                          # Bayesian updating with within but no btwn game transfer
                         "Distinct_stage_BIC" = Bayes_distinct_stage[[id]]$optim$bestval + 1*log(180),
                         "theta_no_btw_tr" = Bayes_distinct_stage[[id]]$optim$bestmem[1],

                          #  No within or between game transfer
                         "Bayes_distinct_no" = Bayes_distinct_no[[id]]$optim$bestval + 1*log(180),
                         "theta_no_tr" =  Bayes_distinct_no[[id]]$optim$bestmem[1],

                          # No distinction between players, transfer within and between
                         "Bayes_same_game" = Bayes_same_game[[id]]$optim$bestval + 1*log(180),
                         "theta_naive" = Bayes_same_game[[id]]$optim$bestmem[1],
                          ###########

@@

# WIth MS results for Bayesian models
exp2_table_results <- table(exp2_results[, "condition"],c("random","TOM_BT","TOM_NBT", "TOM_NT", "QL_states","QLS_within","STEWA_NT","STEWA_Tr")[apply(exp2_results[,c("Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no","QL_states_BIC","QLS_within_Tr_BIC","STEWA_NT_BIC","STEWA_Tr_BIC")],1,which.min)])

 write.csv(exp2_table_results,file="exp2_table_results.csv",row.names = TRUE)
 kable(exp2_table_results)
```

```{r}
exp2_model_comp <- data.frame()
for(id in unique(dat_exp2$human_id)) {
  tdat <- subset(dat_exp2,human_id == id)
  tot_score <- sum(tdat$score)
  early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg" | game =="numbers") )
  tr_score <- sum(early_dat$score)
  id_results <- subset(exp2_results, ID == id)

  # MS BAYES MODELS
  min_BIC <- apply(id_results[,c("Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no","QL_states_BIC","QLS_within_Tr_BIC","STEWA_NT_BIC","STEWA_Tr_BIC")],1,min)

  best_model <- c("random","TOM_BT","TOM_NBT", "TOM_NT", "QL_states","QLS_within","STEWA_NT","STEWA_Tr")[apply(id_results[,c("Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no","QL_states_BIC","QLS_within_Tr_BIC","STEWA_NT_BIC","STEWA_Tr_BIC")],1,which.min)]

@@

write.csv(exp2_model_comp,file="exp2_model_comp.csv",row.names = FALSE)
```

>>>>

```
## Fitting ST_EWA_states WITHOUT transfer 
```{r, cache=TRUE}
# Set seed to random number to check you get same results
set.seed(43)

@@

## Putting all results together 
```{r}

load("exp2_QLS_modelling.Rdata")
load("exp2_QLS_within_Tr.Rdata")
load("exp2_STEWA_NT.Rdata")
load("exp2_STEWA_Tr.Rdata")
load("MBM2_modelling.Rdata")

exp2_results <- data.frame()

@@

                         ########## MS results for Bayesian models
                          # Bayesian updating with between and within game transfer
                         "Distinct_game_BIC" = Bayes_distinct_game[[id]]$optim$bestval + 2*log(180),
                         "theta_transfer" = Bayes_distinct_game[[id]]$optim$bestmem[1],
                         "lambda_transfer" = Bayes_distinct_game[[id]]$optim$bestmem[2],

                          # Bayesian updating with within but no btwn game transfer
                         "Distinct_stage_BIC" = Bayes_distinct_stage[[id]]$optim$bestval + 2*log(180),
                         "theta_no_btw_tr" = Bayes_distinct_stage[[id]]$optim$bestmem[1],
                         "lambda_no_btw_tr" = Bayes_distinct_stage[[id]]$optim$bestmem[2],

                          #  No within or between game transfer
                         "Bayes_distinct_no" = Bayes_distinct_no[[id]]$optim$bestval + 2*log(180),
                         "theta_no_tr" =  Bayes_distinct_no[[id]]$optim$bestmem[1],
                         "lambda_no_tr" =  Bayes_distinct_no[[id]]$optim$bestmem[2],

                          # No distinction between players, transfer within and between
                         # "Bayes_same_game" = Bayes_same_game[[id]]$optim$bestval + 1*log(180),
                         # "theta_naive" = Bayes_same_game[[id]]$optim$bestmem[1],
                         #  ###########

@@

```{r}
# WITH MS results for bayesian models 
# exp2_table_results <- table(exp2_results[, "condition"],c("random","TOM_BT","TOM_NBT", "TOM_NT","ToM_Naive", "QL_states","QLS_within","S_EWA","MBM")[apply(exp2_results[,c("Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no","Bayes_same_game","QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)])
# 
#  write.csv(exp2_table_results,file="exp2_table_results.csv",row.names = TRUE)
#  kable(exp2_table_results)
```

```{r}
exp2_model_comp <- data.frame()
for(id in unique(dat_exp2$human_id)) {
  tdat <- subset(dat_exp2,human_id == id)
  tot_score <- sum(tdat$score)
  tot_time <- sum(tdat$human_rt)
  early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg"))
  #early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg" | game =="numbers") )
  tr_score <- sum(early_dat$score)
  id_results <- subset(exp2_results, ID == id)

  # MS BAYES MODELS
  min_BIC <- apply(id_results[,c("Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no", "QL_states_BIC","QLS_within_Tr_BIC","STEWA_NT_BIC","STEWA_Tr_BIC")],1,min)

  best_model <- c("random","ToM_BT","ToM_NBT", "ToM_NT","QL_states_NT","QLS_within_Tr","STEWA_NT","STEWA_Tr")[apply(id_results[,c("Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no","QL_states_BIC","QLS_within_Tr_BIC","STEWA_NT_BIC","STEWA_Tr_BIC")],1,which.min)]

@@

write.csv(exp2_model_comp,file="exp2_model_comp.csv",row.names = FALSE)

## Calucalting BIC weights 
```{r}

exp2_comp_BICs <- exp2_results[c("ID","Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no", "QL_states_BIC","QLS_within_Tr_BIC","STEWA_NT_BIC","STEWA_Tr_BIC")]

exp2_BIC_weights <- exp2_comp_BICs["ID"]
exp2_BIC_weights[,2:ncol(exp2_comp_BICs)] <- t(apply(exp2_comp_BICs[,2:ncol(exp2_comp_BICs)], 1, function(i) exp(-0.5*(i-min(i)) )))

exp2_BIC_weights[,-1] <- t(apply(exp2_BIC_weights[,-1], 1, function(i) round(i/sum(i),2)))
colnames(exp2_BIC_weights) <- c("ID", "random","ToM_BT","ToM_NBT", "ToM_NT","QL_states_NT","QLS_within_Tr","STEWA_NT","STEWA_Tr")

BIC_comp_table <- as.data.frame(t(colMeans(exp2_BIC_weights[,2:ncol(exp2_BIC_weights)])))

colnames(BIC_comp_table) <- c("random","ToM_BT","ToM_NBT", "ToM_NT","QL_states_NT","QLS_within_Tr","STEWA_NT","STEWA_Tr")
# 
BIC_comp_table

table(exp2_model_comp$Best_model_2)

### 2021-06-04 Experiment_2/exp2_lik_by_trial.Rmd
fixed bugs in report
added report in papaja and softmax to BCH models

  # QLS likelihoods 
  pars_QLS <- unlist(filter(exp2_optim_results, ID == id)%>%select(QL_states_Beta, QL_states_alpha))
  tdat$QLS_lik <-  exp2_QL_states(pars_QLS,tdat,"likelihood_by_trial",0.0, FALSE)

  # QLS within Transfer likelihoods 
  pars_QLS_within <- unlist(filter(exp2_optim_results, ID == id)%>%select(QLS_within_Tr_Beta,QLS_within_Tr_alpha))
  tdat$QLS_lik_within <-  exp2_QL_states(pars_QLS_within,tdat,"likelihood_by_trial",gamma = 0, TRUE)
  #                
  # 
  # Bayes model no transfer likelihoods
  theta_NT <- unlist(filter(exp2_optim_results, ID == id)%>%select(theta_no_tr))
  tdat$Bayes_NT_lik <- Bayes_model_LL(theta_NT, tdat, distinct_opponent = TRUE, generalize = "no",return = "likelihood_by_trial")

  # Bayes model with Transfer likelihood
  theta_Tr <- unlist(filter(exp2_optim_results, ID == id)%>%select(theta_transfer))
  tdat$Bayes_Tr_lik <- Bayes_model_LL(theta_Tr, tdat, distinct_opponent = TRUE, generalize = "game",return = "likelihood_by_trial")

  lik_by_trial_2 <- rbind(lik_by_trial_2,tdat)
}
```

@@

mean_lik_2 <- lik_by_trial_2 %>%
  select(human_id,game,stage,round_condition, round, QLS_lik, QLS_lik_within, Bayes_NT_lik, Bayes_Tr_lik) %>%
  group_by(game,stage,round) %>%
  summarise(mean_QLS_lik = mean(QLS_lik, na.rm = TRUE),
            mean_QLS_within_lik = mean(QLS_lik_within, na.rm = TRUE),
            mean_NT_lik = mean(Bayes_NT_lik, na.rm = TRUE),
            mean_Tr_lik = mean(Bayes_Tr_lik, na.rm = TRUE))

>>>>

  # QLS likelihoods 
  pars_QLS <- unlist(filter(exp2_optim_results, ID == id)%>% dplyr::select(QL_states_Beta, QL_states_alpha))
  tdat$QLS_lik <-  exp2_QL_states(pars_QLS,tdat,"likelihood_by_trial",gamma =0.0, FALSE)

  # QLS within Transfer likelihoods 
  pars_QLS_within <- unlist(filter(exp2_optim_results, ID == id)%>% dplyr::select(QLS_within_Tr_Beta,QLS_within_Tr_alpha))
  tdat$QLS_lik_within <-  exp2_QL_states(pars_QLS_within,tdat,"likelihood_by_trial",gamma = 0, TRUE)
  #                
  # 
  # Bayes model no transfer likelihoods. Assume softmax = TRUE as default. 
  # theta_NT <- unlist(filter(exp2_optim_results, ID == id)%>%select(theta_no_tr))
  # lambda_NT <- unlist(filter(exp2_optim_results, ID == id)%>%select(lambda_no_tr))
  pars_BCH_NT2 <- unlist(filter(exp2_optim_results, ID == id)%>% dplyr::select(theta_no_tr, lambda_no_tr))
  tdat$Bayes_NT_lik <- Bayes_model_LL(pars_BCH_NT2, tdat, distinct_opponent = TRUE, generalize = "no",return = "likelihood_by_trial")

  # Bayes model with Transfer likelihood
  # theta_Tr <- unlist(filter(exp2_optim_results, ID == id)%>%select(theta_transfer))
  pars_BCH_BT2 <- unlist(filter(exp2_optim_results, ID == id)%>% dplyr::select(theta_transfer, lambda_transfer))
  tdat$Bayes_Tr_lik <- Bayes_model_LL(pars_BCH_BT2, tdat, distinct_opponent = TRUE, generalize = "game",return = "likelihood_by_trial")

  lik_by_trial_2 <- rbind(lik_by_trial_2,tdat)
}

write.csv(lik_by_trial_2,file="exp2_lik_by_trial.csv",row.names = FALSE)
```

@@

mean_lik_2 <- lik_by_trial_2 %>%
  dplyr::select(human_id,game,stage,round_condition, round, QLS_lik, QLS_lik_within, Bayes_NT_lik, Bayes_Tr_lik) %>%
  group_by(game,stage,round) %>%
  summarise(mean_QLS_lik = mean(QLS_lik, na.rm = TRUE),
            mean_QLS_within_lik = mean(QLS_lik_within, na.rm = TRUE),
            mean_NT_lik = mean(Bayes_NT_lik, na.rm = TRUE),
            mean_Tr_lik = mean(Bayes_Tr_lik, na.rm = TRUE))
